Homework 6

### 2019-11-12 hw6/MSimonsHW6.tex
Fixing typo in hw6

\item No, because $f(1) = 0$.
\item No, because $g(x) = x^5 + x^4 + 1 = (x^2 + x +1)(x^3 - x + 1)$.
\item Yes.  Since $h(x)$ does not have any roots, it is not divisible
by a polynomial with degree 1.  Therefore, it can only be the product
of an irreducible polynomial with degree 2 and an irreducible polynomial of
degree 3.  The only irreducible polynomial with degree 2 in
$\mathbb{Z}/2\mathbb{Z}$ is $x^2 + x + 1$.  Therefore, if $h(x)$ is reducible,
then it is divisible by $x^2 + x + 1$ in $\mathbb{Z}/2\mathbb{Z}$.  However,
$h(x)$ is NOT divisible by $x^2 + x + 1$, so it must be irreducible.

>>>>

\item No, because $f(1) = 0$.
\item No, because $g(x) = x^5 + x^4 + 1 = (x^2 + x +1)(x^3 - x + 1)$.
\item Yes.  Since $h(x)$ does not have any roots, it is not divisible
by a polynomial with degree 1.  Therefore, it can only be the product
of an irreducible polynomial with degree 2 and an irreducible polynomial of
degree 3.  The only irreducible polynomial with degree 2 in
$(\Z/2\Z)[x]$ is $x^2 + x + 1$.  Therefore, if $h(x)$ is reducible,
then it is divisible by $x^2 + x + 1$ in $(\Z/2\Z)[x]$.  However,
$h(x)$ is NOT divisible by $x^2 + x + 1$, so it must be irreducible.
